\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-06-24 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
updating Section V

\section{Proximal Algorithm}\label{sec:ProxAlgo}
Following \cite{caluya2019TAC}, we solve \eqref{KineticProx} by recursively updating the probability-weighted scattered point clouds $\{\bm{x}_{k}^{i},\tilde{\varrho}_{k}^{i}\}_{i=1}^{N}$ where 
$$\bm{x}_{k}^{i}\equiv\left(\bm{\xi}_{k}^{i},\bm{\eta}_{k}^{i}\right)^{\!\top}, \quad i=1,\hdots,N, \quad k\in\mathbb{N}.$$
Thus, $\tilde{\varrho}_{k}^{i}$ is the joint PDF value obtained from \eqref{KineticProx} at $\bm{x}_{k}^{i}$, the $i$th state sample at the $k$th time step. The schematic of the algorithm is shown in Fig. \ref{fig:BlockDiagm}.

In the numerical simulations reported in Sec. \ref{sec:NumericalSimulations}, the states $\{\bm{x}_{k}^{i}\}_{i=1}^{N}$ are updated by the Euler-Maruyama scheme applied to (\ref{ItoSDEvectorlevel}). If one wishes so, the Euler-Maruyama scheme in Fig. \ref{fig:BlockDiagm} may be replaced by other SDE integrators, see e.g., \cite[Sec. III.B.2, Remark 1]{caluya2019TAC}.

@@

\begin{algorithm}[t]
\caption{Proposed proximal algorithm for $\bm{\varrho}_{k-1}\mapsto\bm{\varrho}_{k}$}
\label{KineticProxAlgorithm}
\begin{algorithmic}[1]
\Procedure{ProxRecursion}{$\bm{\varrho}_{k-1}, h, \varepsilon, N, \delta, L$}
\For{$i=1$ to $N$}
\State $\bm{\zeta}_{k-1}(i) \gets \exp\left(-\left(\bm{\eta}_{k-1}^{i}\right)^{\top}\bm{\eta}_{k-1}^{i}-1\right)$
\For{$j=1$ to $N$}
\State $\bm{C}_{k}(i,j) \gets \parallel\bm{\eta}_{k-1}^{j} - \bm{\eta}_{k}^{i}+ h\nabla U(\bm{\xi}_{k}^{i})\parallel_{2}^{2}$
\State \qquad\quad $+12\bigg\|\dfrac{\bm{\xi}_{k-1}^{j}-\bm{\xi}_{k}^{i}}{h} - \dfrac{\bm{\eta}_{k-1}^{j} + \bm{\eta}_{k}^{i}}{2}\bigg\|_{2}^{2}$
\EndFor
\EndFor
\State $\bm{\Gamma}_{k} \gets \exp\left(-\bm{C}_{k}/2\varepsilon\right)$ \Comment{elementwise exponential}
\State $\bm{z}_{0} \gets {\rm{rand}}_{N\times 1}$ \Comment{random vector of size $N\times 1$}
\State $\bm{z} \gets \left[\bm{z}_{0}, \bm{0}_{N\times(L-1)}\right]$ \Comment{initialize}
\State $\bm{y} \gets \left[\bm{\varrho}_{k-1}\oslash\left(\bm{\Gamma}_{k}\bm{z}_{0}\right), \bm{0}_{N\times(L-1)}\right]$ \Comment{initialize}
\State $\ell = 1$
\While{$\ell\leq L$}
\State $\bm{z}(:,\ell+1) \gets \left(\bm{\zeta}_{k-1}\oslash\left(\bm{\Gamma}_{k}^{\top}\bm{y}(:,\ell)\right)\right)^{\frac{1}{1+2\varepsilon/h}}$
\State $\bm{y}(:,\ell+1) \gets \bm{\varrho}_{k-1} \oslash \left(\bm{\Gamma}_{k}\bm{z}(:,\ell+1)\right)$
\If{$\|\bm{y}(:,\ell+1)-\bm{y}(:,\ell)\|_{2}<\delta$ \& $\|\bm{z}(:,\ell+1)-\bm{z}(:,\ell)\|_{2}<\delta$} \Comment{error within tolerance}
\State break
\Else
\State $\ell \gets \ell + 1$
\EndIf
\EndWhile\\
\Return $\varrho_{k} \gets \bm{z}(:,\ell) \odot \left(\bm{\Gamma}_{k}^{\top}\bm{y}(:,\ell)\right)$ \Comment{proximal update}
\EndProcedure	
\end{algorithmic}
\end{algorithm}

@@

For completeness, the overall proximal algorithm is {\red{given}}. Its convergence guarantees can be found in \cite[Sec. III.C]{caluya2019TAC}.

>>>>

\section{Proximal Algorithm}\label{sec:ProxAlgo}
Following \cite{caluya2019TAC}, we solve \eqref{KineticProx} by recursively updating the probability-weighted scattered point clouds $\{\bm{x}_{k}^{i},\tilde{\varrho}_{k}^{i}\}_{i=1}^{N}$ where 
$$\tilde{\bm{x}}_{k}^{i}:=\left(\bm{\xi}_{k}^{i},\bm{\eta}_{k}^{i}\right)^{\!\top}, \quad i=1,\hdots,N, \quad k\in\mathbb{N}.$$
Thus, $\tilde{\varrho}_{k}^{i}$ is the joint PDF value obtained from \eqref{KineticProx} at $\bm{x}_{k}^{i}$, the $i$th state sample at the $k$th time step. The schematic of the algorithm is shown in Fig. \ref{fig:BlockDiagm}.

In the numerical simulations reported in Sec. \ref{sec:NumericalSimulations}, the states $\{\tilde{\bm{x}}_{k}^{i}\}_{i=1}^{N}$ are updated by the Euler-Maruyama scheme applied to (\ref{ItoSDEvectorlevel}). If one wishes so, the Euler-Maruyama scheme in Fig. \ref{fig:BlockDiagm} may be replaced by other SDE integrators, see e.g., \cite[Sec. III.B.2, Remark 1]{caluya2019TAC}.

@@

\begin{algorithm}[t]
\caption{Proposed proximal algorithm for $\tilde{\bm{\varrho}}_{k-1}\mapsto\tilde{\bm{\varrho}}_{k}$}
\label{algo:KineticProx}
\begin{algorithmic}[1]
\Procedure{ProxRecursion}{$\bm{\varrho}_{k-1}, \tilde{\bm{x}}_{k-1}, \tilde{\bm{x}}_{k}, h, \varepsilon, N, \delta, L$}
\For{$i=1$ to $N$}
\State $\bm{\zeta}_{k-1}(i) \gets \exp\left(-\left(\bm{\eta}_{k-1}^{i}\right)^{\top}\bm{\eta}_{k-1}^{i}-1\right)$
\For{$j=1$ to $N$}
\State $\bm{C}_{k}(i,j) \gets \parallel\bm{\eta}_{k-1}^{j} - \bm{\eta}_{k}^{i}+ h\nabla U(\bm{\xi}_{k}^{i})\parallel_{2}^{2}$
\State \qquad\quad $+12\bigg\|\dfrac{\bm{\xi}_{k-1}^{j}-\bm{\xi}_{k}^{i}}{h} - \dfrac{\bm{\eta}_{k-1}^{j} + \bm{\eta}_{k}^{i}}{2}\bigg\|_{2}^{2}$
\EndFor
\EndFor
\State $\bm{\Gamma}_{k} \gets \exp\left(-\bm{C}_{k}/2\varepsilon\right)$ \Comment{elementwise exponential}
\State $\bm{z}_{0} \gets {\rm{rand}}_{N\times 1}$ \Comment{random vector of size $N\times 1$}
\State $\bm{z} \gets \left[\bm{z}_{0}, \bm{0}_{N\times(L-1)}\right]$ \Comment{initialize}
\State $\bm{y} \gets \left[\tilde{\bm{\varrho}}_{k-1}\oslash\left(\bm{\Gamma}_{k}\bm{z}_{0}\right), \bm{0}_{N\times(L-1)}\right]$ \Comment{initialize}
\State $\ell = 1$
\While{$\ell\leq L$}
\State $\bm{z}(:,\ell+1) \gets \left(\bm{\zeta}_{k-1}\oslash\left(\bm{\Gamma}_{k}^{\top}\bm{y}(:,\ell)\right)\right)^{\frac{1}{1+2\varepsilon/h}}$
\State $\bm{y}(:,\ell+1) \gets \tilde{\bm{\varrho}}_{k-1} \oslash \left(\bm{\Gamma}_{k}\bm{z}(:,\ell+1)\right)$
\If{$\|\bm{y}(:,\ell+1)-\bm{y}(:,\ell)\|_{2}<\delta$ \& $\|\bm{z}(:,\ell+1)-\bm{z}(:,\ell)\|_{2}<\delta$} \Comment{error within tolerance}
\State break
\Else
\State $\ell \gets \ell + 1$
\EndIf
\EndWhile\\
\Return $\tilde{\bm{\varrho}}_{k} \gets \bm{z}(:,\ell) \odot \left(\bm{\Gamma}_{k}^{\top}\bm{y}(:,\ell)\right)$ \Comment{proximal update}
\EndProcedure	
\end{algorithmic}
\end{algorithm}

@@

For completeness, the proximal algorithm for updating $\{\tilde{\varrho}_{k-1}^{i}\}_{i=1}^{N}\mapsto\{\tilde{\varrho}_{k}^{i}\}_{i=1}^{N}$ is outlined in Algorithm \ref{algo:KineticProx}. Its convergence guarantees can be found in \cite[Sec. III.C]{caluya2019TAC}.
